---
title: "01-exercises"
author: "Christopher Brown"
date: "April 6, 2016"
output: html_document
---


## Exercise 1:

Write a function (f) that get a vector of numbers, **x**, and returns a vector of numbers such that each element containing the product of every element of x except the element of x with the same index. 


### Example 

    > x <- c( 1, 5, 2, 8 ) 
    > f(x) 
    [1] 80 16 40 10
    # 5*2*8, 1*2*8, 1*5*8, 1*2*5  


### Solution 

```{r}

  
  x <- c( 1, 5, 2, 8 )
  y<- 1:length(x)
  y
  prod (x)/x[y]


```
    
x

## Exercise 2

Write a function f(x) to accept an integer vector, and returns a vector with those numbers except for: 
   multiples of 3 replaced by "Fizz"? 
   multiples of 5 replaced by "Buzz" 
   multiples of 3 and 5 replaced by "FizzBuzz""
   
### Example

    > x <- 1:20
    > f(1:20) 
    # 1 2 Fizz 4 Buzz Fizz 7 8 Fizz Buzz 11 Fizz 13 14 FizzBuzz 16 17 Fizz 19 Buzz


### Solution

```{r}
  

  x <- 1:20
  div3 <- x%%3 ==0
  div5 <- x%%5 ==0
  div15 <- x%%15 ==0
  x [which (div3==TRUE)] <- 'Fizz'
  x [which (div5==TRUE)] <- 'Buzz'
  x [which (div15==TRUE)] <- 'Fizzbuzz'
 x

```
