---
title: "Assingment NYC Flight Data"
author: "Beatrice Wee"
date: "April 8, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## NYC Flight Data

Your job is to create a "rectangular" table useful for modeling from flight data. 
In the folder `02-fundamentals/data` there are four CSV files: `flights.csv`, 
`airports.csv`, `planes.csv` and `weather.csv`.  Join/merge these tables such 
that there is one rectangular table with one row for each flight. 


Put code in each of the sections provided.

## 1. Read Data

Using the `readr` package read the `flights` data.

```{r}
flights <- read.csv("flights.csv")
head (flights)
tail (flights)
summary (flights)
str(flights)
```

## Numeric Variables  

Plot a histogram of arrival delays and departure delays 

```{r}
library(ggplot2)
x <- flights["arr_delay"] + flights["dep_delay"]
flights$totaldelay <- x
hist<- ggplot(data=flights, aes(x)) + geom_histogram(breaks=seq(2, 200, by =2), col = "grey", fill="steelblue")
hist
```

## Scatterplot

Plot a scatterplot of date vs arrival delay 

```{r}
library(ggplot2)
library(lubridate)
flights$date <- as.Date(with(flights, paste(year, month, day,sep="-")), "%Y-%m-%d")
ggplot(flights, aes(flights$date, arr_delay))+ geom_point()

```



## Create tables for Categorical Variables

Create a `table`, counting the flights by origin airports and carrier.

```{r}
a <- table(flights$origin)
b <- table (flights$carrier)
a.df <- as.data.frame(a)
a.df
b.df <- as.data.frame(b)
b.df
```


## Join Data

**Read** in the other data sets. Use methods to join the data together to create a single table containing one record per row.  (HINT: see `?data.table` or `?dplyr::join`)

```{r}

```



